Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-13 doc/JFLA2022/paper.tex
content in book comparison

>>>>

We believe that current Coq books can broadly be divided into two categories:
\begin{itemize}
\item \emph{Executable books} that are in effect large, well-commented Coq programs from which other representations of the material (HTML, PDF) are derived using tools.
\item \emph{Traditional books} generated from documentation languages such as LaTeX that are accompanied by standalone Coq formalizations.
\end{itemize}
